### 2017-12-05 manuscript.rmd
quick edits to first two paragraphs

Siphonophores (Fig. 1) are among the most abundant gelatinous predators in the open ocean, and play an important ecological role in oceanic waters [@pugh1984diel;@pugh1997vertical; @williams1981vertical;@purcell1981dietary;@pages2001gelatinous]. Siphonophores, which belong to Hydrozoa (Cnidaria), are found at all depths in the ocean. The Portuguese man of war *Physalia physalis* floats at the surface and, as a result, is the most familiar siphonophore species [@Totton1960]. Most siphonophores species are planktonic, living in the midwater where some grow to be longer than 30 meters in length [@mackie1987siphonophore]. There is also a small clade of benthic siphonophores, the Rhodaliidae [@pugh1983benthic], that are tethered to the bottom for part of their lives. In all, there are currently 188 valid described species.

Siphonophores remain poorly known, in large part because they are fragile and difficult to collect. They have, however, been of great interest for more than 150 years due to their very unique structure and development [@mapstone2014global;@mackie1987siphonophore]. Like many other cnidarians, they are colonial -- they grow by incomplete asexual reproduction. Each siphonophore colony arises from a single embryo that forms the protozooid, the first body. A growth zone then arises that asexually produces other genetically identical zooids [@carre1969etude; @carre1991complete; @carre1967; @carre1995ordre]. These zooids are each homologous to a solitary animal, but are physiologically integrated [@totton1965synopsis; @mackie1987siphonophore; @dunn2006evolution]. Siphonophores differ significantly from all other colonial animals in terms of colony structure, development, and the degree to which they are functionally specialized [@Beklemishev1969;@cartwright2010character]. Each zooid is functionally specialized for a particular task (e.g feeding, reproducing, swimming) (fig. 2) [@dunn2006evolution], and they are arranged in a repeating,  species-specific pattern.

>>>>

Siphonophores (Fig. 1) are among the most abundant gelatinous predators in the open ocean, and play important ecological roles in oceanic waters [@pugh1984diel;@pugh1997vertical; @williams1981vertical;@purcell1981dietary;@pages2001gelatinous]. Siphonophores, which belong to Hydrozoa (Cnidaria), are found at all depths in the ocean. The most familiar siphonophore species is the Portuguese man of war *Physalia physalis*, which floats at the surface and can wash up conspicuously onto beaches [@Totton1960]. Most siphonophore species are planktonic, living in the water column, where some grow to be up to 30 meters in length [@mackie1987siphonophore]. There is also a small clade of benthic siphonophores, the Rhodaliidae [@pugh1983benthic], that are tethered to the bottom for part of their lives. In all, there are currently 188 valid described species.

Siphonophores remain poorly known, in large part because they are fragile and difficult to collect. They have, however, been of great interest for more than 150 years due to their very unique structure and development [@mapstone2014global;@mackie1987siphonophore]. Like many other cnidarians, they are colonial: they grow by incomplete asexual reproduction. Each siphonophore colony arises from a single embryo that forms the protozooid, the first body. A growth zone then arises that asexually produces other genetically identical zooids [@carre1969etude; @carre1991complete; @carre1967; @carre1995ordre]. These zooids are each homologous to a solitary animal, but are physiologically integrated [@totton1965synopsis; @mackie1987siphonophore; @dunn2006evolution]. Siphonophores differ significantly from all other colonial animals in colony structure, development, and the degree to which they are functionally specialized [@Beklemishev1969;@cartwright2010character]. Each zooid is functionally specialized for a particular task (*e.g.*, feeding, reproducing, swimming) (fig. 2) [@dunn2006evolution], and they are arranged in a repeating,  species-specific pattern.
